\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{ragged2e}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue
}

\newcommand{\pathlink}[1]{\href{run:#1}{\nolinkurl{#1}}}
\newcommand{\runlink}[2]{\href{run:#1}{#2}}
\newcommand{\designid}[1]{\nolinkurl{#1}}
\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}
\renewcommand{\arraystretch}{1.15}
\setlength{\tabcolsep}{4pt}

\title{MEEN 305 Print-Test Shortlist}
\author{}
\date{2026-04-23}

\begin{document}
\maketitle

\section*{Bottom Line}

The current project-correct design to print first is
\designid{continuous_uniform_both_load_cases_9in_corrected}. It is the
active source-of-truth design in this repo because it explicitly uses the
correct beam geometry: total length \(9.0\ \mathrm{in}\)
\((228.6\ \mathrm{mm})\), supports at \(x=0.5\ \mathrm{in}\)
\((12.7\ \mathrm{mm})\) and \(x=8.5\ \mathrm{in}\)
\((215.9\ \mathrm{mm})\), and the Team 6 load cases.

The older archived designs are still useful as comparison specimens, but they
should be treated as \emph{benchmark prints}, not as the final project answer,
because the repo notes state that many archived outputs predate the full
9-inch support-placement correction.

\section*{What To Do Next}

\begin{enumerate}
  \item Print and test
  \texttt{continuous\_uniform\_both\_load\_cases\_9in\_corrected} first. This
  is the only design in the shortlist that is both current and project-correct.
  \item Print \texttt{optimization\_final} as the archived baseline. It is the
  cleanest older ``final-style'' candidate and remains one of the best fully
  documented print-friendly references in the repo.
  \item Print \texttt{optimization\_revised\_symmetric\_light} next if you want
  a cleaner symmetric comparison that still stays near the FoS \(=1.5\) target.
  \item Print \texttt{optimization\_v2\_Q7777} as the aggressive lightweight
  benchmark. It is one of the lightest archived Team-6-style passing options.
  \item If you want a fifth print, use
  \texttt{optimization\_revised\_symmetric\_balanced} as a smooth, symmetric
  control specimen.
  \item Do \emph{not} spend a print on both \texttt{optimization\_final} and
  \texttt{optimization\_connected\_v2\_6060}; their stored geometry and metrics
  are effectively identical in this repo.
  \item Use one print profile for all test pieces so the comparison is fair,
  then record actual mass, max elastic deflection, visible failure location,
  and whether failure starts near the predicted governing section.
  \item After testing, update the final report with corrected 9-inch results
  plus a short validation table comparing predicted and measured behavior.
\end{enumerate}

\section*{Common Material And Print Assumptions}

These are the analysis assumptions used by the active solver in
\pathlink{scripts/beam_solver.py}.

\small
\begin{tabularx}{\textwidth}{@{}p{0.28\textwidth}YY@{}}
\toprule
Property & Imperial & Metric \\
\midrule
Material family & PLA & PLA \\
Printer basis & 0.4 mm nozzle, about 40\% rectilinear infill & 0.0157 in nozzle, about 40\% rectilinear infill \\
Beam length & \(9.0\ \mathrm{in}\) total, \(8.0\ \mathrm{in}\) support span & \(228.6\ \mathrm{mm}\) total, \(203.2\ \mathrm{mm}\) support span \\
Support locations & \(x_A=0.5\ \mathrm{in}\), \(x_B=8.5\ \mathrm{in}\) & \(x_A=12.7\ \mathrm{mm}\), \(x_B=215.9\ \mathrm{mm}\) \\
Load Case 1 & \(5.0\ \mathrm{lbf}\) at \(4.0\ \mathrm{in}\) from A & \(22.24\ \mathrm{N}\) at \(101.6\ \mathrm{mm}\) from A \\
Load Case 2 & \(8.0\ \mathrm{lbf}\) at \(5.0\ \mathrm{in}\) from A & \(35.59\ \mathrm{N}\) at \(127.0\ \mathrm{mm}\) from A \\
Nominal elastic modulus & \(500{,}000\ \mathrm{psi}\) & \(3447.38\ \mathrm{MPa}\) \\
Nominal allowable stress & \(4{,}000\ \mathrm{psi}\) & \(27.58\ \mathrm{MPa}\) \\
Weight density & \(0.045\ \mathrm{lbf/in^3}\) & \(12.22\ \mathrm{kN/m^3}\) (about \(1.25\ \mathrm{g/cm^3}\) mass density) \\
Orientation factor & \(0.70\) & \(0.70\) \\
Infill factor & \(0.85\) & \(0.85\) \\
Effective modulus used in solver & \(297{,}500\ \mathrm{psi}\) & \(2051.19\ \mathrm{MPa}\) \\
Effective allowable stress used in solver & \(2{,}380\ \mathrm{psi}\) & \(16.41\ \mathrm{MPa}\) \\
Hard printability floor & wall thickness \(\ge 0.040\ \mathrm{in}\), dimension \(\ge 0.150\ \mathrm{in}\) & wall thickness \(\ge 1.016\ \mathrm{mm}\), dimension \(\ge 3.81\ \mathrm{mm}\) \\
Durability screen target & residual ligament \(\ge 0.080\ \mathrm{in}\) & residual ligament \(\ge 2.032\ \mathrm{mm}\) \\
\bottomrule
\end{tabularx}
\normalsize

\section*{Recommended Print Queue}

If you only want four prints, stop after Item 4. Item 5 is the optional control.

\small
\begin{longtable}{@{}p{0.05\textwidth}p{0.25\textwidth}p{0.15\textwidth}p{0.09\textwidth}p{0.15\textwidth}p{0.24\textwidth}@{}}
\toprule
Order & Design & Weight [lbf / N] & Min FoS & Max Defl. [in / mm] & Why it belongs in the test set \\
\midrule
\endhead
1 & \designid{continuous_uniform_both_load_cases_9in_corrected} & 0.04079 / 0.181 & 1.503 & 0.16121 / 4.10 & Current project-correct reference design; must-print. \\
2 & \designid{optimization_final} & 0.03018 / 0.134 & 1.634 & 0.12226 / 3.11 & Best archived final-style benchmark with full package and clean printability. \\
3 & \designid{optimization_revised_symmetric_light} & 0.03254 / 0.145 & 1.515 & 0.13453 / 3.42 & Best symmetric near-target comparator. \\
4 & \designid{optimization_v2_Q7777} & 0.03454 / 0.154 & 1.522 & 0.11608 / 2.95 & Lightest archived Team-6-style passing option; useful aggressive benchmark. \\
5 & \designid{optimization_revised_symmetric_balanced} & 0.02649 / 0.118 & 1.863 & 0.09424 / 2.39 & Optional smooth control specimen; easiest geometry family to compare against. \\
\bottomrule
\end{longtable}
\normalsize

\section*{Design Notes}

\subsection*{1. Corrected 9 in Reference}

\textbf{Why first:} this is the repo's current recommended design in
\pathlink{docs/notes/current_design_selection.md}. It is the one that matches
the corrected 9-inch beam with supports at \(x=0.5\ \mathrm{in}\)
\((12.7\ \mathrm{mm})\) and \(x=8.5\ \mathrm{in}\)
\((215.9\ \mathrm{mm})\).

\small
\begin{tabularx}{\textwidth}{@{}p{0.31\textwidth}Y@{}}
\toprule
Property & Value \\
\midrule
Design ID & \designid{continuous_uniform_both_load_cases_9in_corrected} \\
Widths & \(0.521 / 0.294 / 0.521\ \mathrm{in}\) \\ \(13.24 / 7.48 / 13.24\ \mathrm{mm}\) \\
Heights & \(0.659 / 0.713 / 0.659\ \mathrm{in}\) \\ \(16.73 / 18.11 / 16.73\ \mathrm{mm}\) \\
Wall thickness & \(0.0508\ \mathrm{in}\) \\ \(1.290\ \mathrm{mm}\) \\
Web openings & \(0 / 0 / 0\) \\
Governing case & Load Case 2 at global \(x=5.5\ \mathrm{in}\) \\ global \(x=139.7\ \mathrm{mm}\) \\
Minimum FoS & \(1.503\) \\
Maximum deflection & \(0.16121\ \mathrm{in}\) \\ \(4.095\ \mathrm{mm}\) \\
\bottomrule
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{@{}p{0.22\textwidth}Y@{}}
\toprule
File & Link \\
\midrule
Package folder & \runlink{designs/packages/continuous_design_deliverables_9in_corrected/continuous_uniform_both_load_cases_9in_corrected}{Open package folder} \\
STL & \runlink{designs/packages/continuous_design_deliverables_9in_corrected/continuous_uniform_both_load_cases_9in_corrected/continuous_uniform_both_load_cases_9in_corrected.stl}{Open STL} \\
Best design JSON & \runlink{designs/packages/continuous_design_deliverables_9in_corrected/continuous_uniform_both_load_cases_9in_corrected/best_design.json}{Open JSON} \\
Report & \runlink{designs/packages/continuous_design_deliverables_9in_corrected/continuous_uniform_both_load_cases_9in_corrected/optimization_report.md}{Open report} \\
\bottomrule
\end{tabularx}
\normalsize

\subsection*{2. Archived Final Baseline}

\textbf{Why second:} this is the cleanest archived ``final'' comparison print.
The archived printability note explicitly calls it a defensible final choice.

\small
\begin{tabularx}{\textwidth}{@{}p{0.31\textwidth}Y@{}}
\toprule
Property & Value \\
\midrule
Design ID & \designid{optimization_final} \\
Widths & \(0.446 / 0.350 / 0.572\ \mathrm{in}\) \\ \(11.32 / 8.90 / 14.54\ \mathrm{mm}\) \\
Heights & \(1.051 / 0.559 / 0.530\ \mathrm{in}\) \\ \(26.69 / 14.21 / 13.46\ \mathrm{mm}\) \\
Wall thickness & \(0.0600\ \mathrm{in}\) \\ \(1.524\ \mathrm{mm}\) \\
Web openings & \(0.621 / 0.525 / 0.297\) \\
Governing case & Load Case 2 at \(x=5.0\ \mathrm{in}\) \\ \(x=127.0\ \mathrm{mm}\) \\
Minimum FoS & \(1.634\) \\
Maximum deflection & \(0.12226\ \mathrm{in}\) \\ \(3.105\ \mathrm{mm}\) \\
\bottomrule
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{@{}p{0.22\textwidth}Y@{}}
\toprule
File & Link \\
\midrule
Package folder & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_final}{Open package folder} \\
STL & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_final/optimization_final.stl}{Open STL} \\
Best design JSON & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_final/best_design.json}{Open JSON} \\
Report & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_final/optimization_report.md}{Open report} \\
\bottomrule
\end{tabularx}
\normalsize

\subsection*{3. Symmetric Near-Target Comparator}

\textbf{Why third:} this is the best archived symmetric design that still stays
very close to the FoS target. It is useful if you want a specimen that is easy
to explain and visually cleaner than the more asymmetric archived runs.

\small
\begin{tabularx}{\textwidth}{@{}p{0.31\textwidth}Y@{}}
\toprule
Property & Value \\
\midrule
Design ID & \designid{optimization_revised_symmetric_light} \\
Widths & \(0.535 / 0.362 / 0.535\ \mathrm{in}\) \\ \(13.58 / 9.21 / 13.58\ \mathrm{mm}\) \\
Heights & \(0.453 / 0.493 / 0.453\ \mathrm{in}\) \\ \(11.50 / 12.52 / 11.50\ \mathrm{mm}\) \\
Wall thickness & \(0.0600\ \mathrm{in}\) \\ \(1.524\ \mathrm{mm}\) \\
Web openings & \(0.000 / 0.266 / 0.000\) \\
Governing case & Load Case 2 at \(x=5.0\ \mathrm{in}\) \\ \(x=127.0\ \mathrm{mm}\) \\
Minimum FoS & \(1.515\) \\
Maximum deflection & \(0.13453\ \mathrm{in}\) \\ \(3.417\ \mathrm{mm}\) \\
\bottomrule
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{@{}p{0.22\textwidth}Y@{}}
\toprule
File & Link \\
\midrule
Package folder & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_revised_symmetric_light}{Open package folder} \\
STL & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_revised_symmetric_light/optimization_revised_symmetric_light.stl}{Open STL} \\
Best design JSON & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_revised_symmetric_light/best_design.json}{Open JSON} \\
Report & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_revised_symmetric_light/optimization_report.md}{Open report} \\
\bottomrule
\end{tabularx}
\normalsize

\subsection*{4. Aggressive Lightweight Benchmark}

\textbf{Why fourth:} among the archived Team-6-style designs that still pass
cleanly, this is the lightweight aggressive benchmark. It is not the current
final answer, but it is still a strong comparison specimen.

\small
\begin{tabularx}{\textwidth}{@{}p{0.31\textwidth}Y@{}}
\toprule
Property & Value \\
\midrule
Design ID & \designid{optimization_v2_Q7777} \\
Widths & \(0.823 / 0.350 / 0.350\ \mathrm{in}\) \\ \(20.90 / 8.89 / 8.89\ \mathrm{mm}\) \\
Heights & \(0.959 / 0.727 / 0.606\ \mathrm{in}\) \\ \(24.37 / 18.46 / 15.38\ \mathrm{mm}\) \\
Wall thickness & \(0.0600\ \mathrm{in}\) \\ \(1.524\ \mathrm{mm}\) \\
Web openings & \(0.334 / 0.650 / 0.276\) \\
Governing case & Load Case 2 at \(x=5.0\ \mathrm{in}\) \\ \(x=127.0\ \mathrm{mm}\) \\
Minimum FoS & \(1.522\) \\
Maximum deflection & \(0.11608\ \mathrm{in}\) \\ \(2.949\ \mathrm{mm}\) \\
\bottomrule
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{@{}p{0.22\textwidth}Y@{}}
\toprule
File & Link \\
\midrule
Data folder & \runlink{archive/deprecated_assets/optimization_v2_Q7777}{Open data folder} \\
STL & \runlink{archive/deprecated_assets/models_3d/optimization_v2_q7777.stl}{Open STL} \\
Best design JSON & \runlink{archive/deprecated_assets/optimization_v2_Q7777/best_design.json}{Open JSON} \\
Report & \runlink{archive/deprecated_assets/optimization_v2_Q7777/optimization_report.md}{Open report} \\
\bottomrule
\end{tabularx}
\normalsize

\subsection*{5. Symmetric Balanced Control (Optional)}

\textbf{Why optional:} this is a good control print when you want a smooth,
very symmetric geometry with comfortable margin. It is lighter than the other
archived candidates listed here, but it is also more conservative than the
near-target options because the minimum FoS stays well above 1.5.

\small
\begin{tabularx}{\textwidth}{@{}p{0.31\textwidth}Y@{}}
\toprule
Property & Value \\
\midrule
Design ID & \designid{optimization_revised_symmetric_balanced} \\
Widths & \(0.350 / 0.411 / 0.350\ \mathrm{in}\) \\ \(8.89 / 10.44 / 8.89\ \mathrm{mm}\) \\
Heights & \(0.785 / 0.777 / 0.785\ \mathrm{in}\) \\ \(19.95 / 19.74 / 19.95\ \mathrm{mm}\) \\
Wall thickness & \(0.0604\ \mathrm{in}\) \\ \(1.534\ \mathrm{mm}\) \\
Web openings & \(0.677 / 0.631 / 0.677\) \\
Governing case & Load Case 2 at \(x=5.0\ \mathrm{in}\) \\ \(x=127.0\ \mathrm{mm}\) \\
Minimum FoS & \(1.863\) \\
Maximum deflection & \(0.09424\ \mathrm{in}\) \\ \(2.394\ \mathrm{mm}\) \\
\bottomrule
\end{tabularx}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{@{}p{0.22\textwidth}Y@{}}
\toprule
File & Link \\
\midrule
Package folder & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_revised_symmetric_balanced}{Open package folder} \\
STL & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_revised_symmetric_balanced/optimization_revised_symmetric_balanced.stl}{Open STL} \\
Best design JSON & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_revised_symmetric_balanced/best_design.json}{Open JSON} \\
Report & \runlink{archive/deprecated_assets/relevant_design_packages/optimization_revised_symmetric_balanced/optimization_report.md}{Open report} \\
\bottomrule
\end{tabularx}
\normalsize

\section*{Notes On Scope}

\begin{itemize}
  \item The corrected design is the one to cite in the final report.
  \item The archived designs are still worth printing because they cover
  different geometry strategies: open-web asymmetric, clean symmetric, and
  aggressive lightweight variants.
  \item I intentionally did not include archived designs such as
  \designid{optimization_v2_E} or \designid{optimization_v2_F} in the main
  print queue because their stored load cases do not match the current Team 6
  loading used by the active corrected workflow.
\end{itemize}

\end{document}
